Named Entity Recognition as Structured Prediction

### 2012-11-09 doc/report/paper.tex
++

\begin{enumerate}
\item \parbox[t]{2.4in}{ (a)~\Tree  \label{bos}
   [.NP [ [.DT the ] [.N\1 [.N Bank ] [.PP [.P of ] [.NP Scotland ] ] ] ] ]}
\parbox[t]{2in}{ (b)~\Tree 
   [.NP  [.N\1 [.N\1  \qroof{Kurt Cobain}.N  ]  [.PP [.P of ] [.N\1 [.N\1 [.N Nirvana ] ] ] ] ] ]  } \label{Nirvana}
\end{enumerate}

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test dataset was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro2002conll} and the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195}.
for Spanish \& Dutch and English \& German respectively. The ConNLL shared tasks are organised challenges, where the organiser propose a task and provide the
training and test data. For 2002/2003 it was Named Entity Recognition. Also we base our system on the approach that won the challenge for English and German in 2003. 
The baseline rate for all languages was produced by a system, that had a unique class in the training data. In case that a phrase was part of more than one entity, 
the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
The data is annotated with POS-tags and NE-tags, as well as Bio-tags that indicate the position in the Named Entity. 
% A baseline rate was computed for the English and the
% German test sets. It was produced by a system which
% only identified entities which had a unique class in
% the training data. If a phrase was part of more than
% one entity, the system would select the longest one.
% All systems that participated in the shared task have
% outperformed the baseline system.
% For all the Fβ=1 rates we have estimated sig-
% nificance boundaries by using bootstrap resampling
% (Noreen, 1989). From each output file of a system,
% 250 random samples of sentences have been chosen
% and the distribution of the Fβ=1 rates in these sam-
% ples is assumed to be the distribution of the perfor-
% mance of the system. We assume that performance
% A is significantly different from performance B if A
% is not within the center 90% of the distribution of B.

The baseline for \emph{Named Entity Recognition} in the four different languages is visualised in table \
\begin{table}[h!]
\scriptsize
\begin{tabular}{|l|l|l|l|}
\hline
\bf Language & \bf Precision & \bf Recall & \bf $F_1$-measure \\ \hline
Spanish &             26.27\% & 56.48\% & 35.86\%        \\
Dutch  &             64.38\%  &45.19\%    & 53.10\%  \\
English &              71.91\%& 50.90\%  & 59.61 $\pm$ 1.2\%\\
German &      31.86\%  & 28.89\% & 30.30  $\pm$ 1.3\% \\
\hline
\end{tabular}
\caption{NER Baseline}
\label{table:Base}
\end{table}

@@

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:} O O O O ORG  O  O O O O O PER PER O  \label{PredEx1b} \\
\caption{Input and predicted structure for the Named Entity task.}

>>>>

\begin{enumerate}
\item \parbox[t]{2.4in}{ (a)~\Tree  
   [.NP [ [.DT the ] [.N\1 [.N Bank ] [.PP [.P of ] [.NP Scotland ] ] ] ] ] } \label{bos}
\parbox[t]{2in}{ (b)~\Tree 
   [.NP  [.N\1 [.N\1  \qroof{Kurt Cobain}.N  ]  [.PP [.P of ] [.N\1 [.N\1 [.N Nirvana ] ] ] ] ] ]  } \label{Nirvana}
\end{enumerate}

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro} and 
the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. 
Our approach is based on the system that won the challenge for English and German in 2003.

% A baseline rate was computed for the English and the
% German test sets. It was produced by a system which
% only identified entities which had a unique class in
% the training data. If a phrase was part of more than
% one entity, the system would select the longest one.
% All systems that participated in the shared task have
% outperformed the baseline system.
% For all the Fβ=1 rates we have estimated sig-
% nificance boundaries by using bootstrap resampling
% (Noreen, 1989). From each output file of a system,
% 250 random samples of sentences have been chosen
% and the distribution of the Fβ=1 rates in these sam-
% ples is assumed to be the distribution of the perfor-
% mance of the system. We assume that performance
% A is significantly different from performance B if A
% is not within the center 90% of the distribution of B.

\begin{table}[h!]
\scriptsize
\begin{tabular}{|l|l|l|l|}
\hline
\bf Language & \bf Precision & \bf Recall & \bf $F_1$-measure \\ \hline
Spanish &             26.27\% & 56.48\% & 35.86\%        \\
Dutch  &             64.38\%  &45.19\%    & 53.10\%  \\
English &              71.91\%& 50.90\%  & 59.61 $\pm$ 1.2\%\\
German &      31.86\%  & 28.89\% & 30.30  $\pm$ 1.3\% \\
\hline
\end{tabular}
\caption{NER Baseline}
\label{table:Base}
\end{table}

@@

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:}  O   O      O     0 ORG  O  O     O     O       O        O PER   PER  O  \label{PredEx1b} \\
\caption{Input and predicted structure for the Named Entity task.}
